---
title: "Temp_Time_Series"
author: "Sam Bogan"
date: "6/23/2021"
output: github_document
---

This is an R Markdown written by Sam Bogan that reads in, wrangles, summarizes, and analyzes time series temperatures collected from n = 3 per site supralittoral splash pools occupied by *Tigriopus californicus* across 4 sites in coastal California (see README). Data were recorded by TidBit MX5000 temperature loggers made by Onset Computer Corp between 2019 - 2021. 

```{r setup, include=FALSE}

knitr::opts_knit$set(root.dir = '~/Documents/GitHub/HotOnes_Tigriopus/TidBits/')

```

#Identify measurements to filter out

```{r}

# Load packages
library(tidyverse)
library(Rmisc)
library(lubridate)
library(data.table)
library(tibbletime)
library(mapdata)
library(ggpubr)

# Read csv describing periods where loggers broke or were aerially exposed
TidBit_meta_df <- read.csv("~/Documents/GitHub/HotOnes_Tigriopus/Temp_Time_Series/Input_files/TidBit_Deployment_Check_History.csv" )

# Print metadata sheet
TidBit_meta_df

## Filter out periods where logger may have been aerially exposed due to evaporation of pool
# Start by outputing rows in metadata signifying post-date filtering
filt_post_dates <- filter( TidBit_meta_df, Filter_Post_Date == "Yes" )

# Print dates
filt_post_dates

# Create variables for filtering
logger_to_filter <- as.character( filt_post_dates$Logger )
date_to_filter_past <- as.Date( filt_post_dates$Date, "%m/%d/%y" )

```

#Read and wrangle raw data

```{r}

# Move to input data directory for tempm time series
setwd( "~/Documents/GitHub/HotOnes_Tigriopus/TidBits/" )

# Get the files names
temps <- list.files( pattern = "*0.csv" )

# Read in .csv files listed in temps
mytemps <- lapply( temps, read.csv )

# Correct df names from mytemps
names( mytemps ) <- gsub( " .*",
                          "",
                          temps )

# Remove unecessary columns and standardize column number
# mytemps <- lapply( mytemps, function ( y ) { y <- select( y, c( 1, 2 ) ) } )

# Filter out contiously aerially-exposed measurements in BRM2
mytemps$BMR2 <- dplyr::filter( mytemps$BMR2, as.Date( Date.Time..GMT..0800, "%m/%d/%y" ) < as.Date( date_to_filter_past ) )

# Data from PTD3 must be filtered following 02/02/2021 due to damage and miscalibration
mytemps$PTD3 <- dplyr::filter( mytemps$PTD3, as.Date(  mytemps$PTD3$Date.Time..GMT..0700, "%m/%d/%y" ) < as.Date( "2021-02-02 00:00:00" ) )

# Combine all temp dfs
all_temps <- rbindlist( mytemps, 
                        idcol = "Logger" )

# Remove rows where temp is empty
all_temps <- all_temps[ !(is.na( all_temps$Temp....F. ) | 
                            all_temps$Temp....F.  == "" ), ]

# Create site variable
all_temps$Site <- gsub( "[1-9]+", 
                        "", 
                        all_temps$Logger )

# Fix column names
names( all_temps )[ names( all_temps ) == "Date.Time..GMT..0800"] <- "Date_Time"
names( all_temps )[ names( all_temps ) == "Temp....F."] <- "Temp"

# Convert temp to celcius
all_temps$Temp <- round( ( ( all_temps$Temp - 32 ) * ( 5 / 9 ) ),
                         digits = 2 )

# Create date variable
all_temps$Date <- as.Date( all_temps$Date_Time, "%m/%d/%y" )

# Ensure that Date_Time variable is in date-time format
all_temps$Date_Time <- mdy_hm( all_temps$Date_Time )

# Create month variable
all_temps$Month <- month( all_temps$Date )

all_temps$Site <- gsub("RM", "RMR", gsub("RMR", "RM", all_temps$Site))
all_temps$Site <- gsub("SCB", "SC", all_temps$Site)
all_temps$Site <- gsub("PTDB", "PTD", all_temps$Site)

table(all_temps$Site)

# Create latitude index
lat_index <- data.frame( Site = c( "BMR", "SC", "RMR", "PTD" ),
                         Lat = c( 38.316375,
                                  36.965681,
                                  35.540147,
                                  34.002089 ) )
# Merge lat index with temp df
all_temps <- merge( all_temps,
       lat_index,
       by = "Site" )

table(all_temps$Site)

```

How do transport temperatures during selection experiment collections compare to field temperatures?

```{r}

# Aug 21 transport mean = 19.96 C
# Feb 22 transport mean = 13.00 C

# Filter TidBit temps so that they span 3 weeks prior to Aug and Feb collections
Aug_21d_prior_temps <- filter(all_temps, Date > as.Date("2021-07-16") & 
                                Date < as.Date("2021-08-06"))

Aug_offset <- 19.96 - mean(Aug_21d_prior_temps$Temp)
Aug_offset


Feb_21d_prior_temps <- filter(all_temps, Date > as.Date("2022-01-26") & 
                                Date < as.Date("2022-02-16"))

Feb_offset <- 13.00 - mean(Feb_21d_prior_temps$Temp)
Feb_offset

```


#Plot filtered temperatures

```{r}

# Filter to common earliest and latest dates for all loggers before plot means: one day after PTD deployment
all_temps_filt <- filter( all_temps, 
                          Date > as.Date( "2020-03-12" ),
                          Date < as.Date( "2023-03-01" ) )

# Filter out miscalibrated temps
all_temps_filt <- filter( all_temps,Temp < 80)

# Estimate daily means
mean_temps <- summarySE( measurevar = "Temp",
                         groupvars = c( "Site", "Date", "Lat", "Month" ),
                         data = all_temps_filt )

# Convert mean date to datetime variable
names( mean_temps )[ names( mean_temps ) == "Date"] <- "Date_Time"
mean_temps$Date_Time <- as_datetime( mean_temps$Date_Time )

# Estimate site means
site_temps <- summarySE( measurevar = "Temp",
                         groupvars = c( "Site", "Lat" ),
                         data = all_temps_filt )

# Estimate site means by month
site_month_temps <- summarySE( measurevar = "Temp",
                         groupvars = c( "Site", "Lat", "Month" ),
                         data = all_temps_filt )

# Plot daily means over time, colored by site
ggplot( data = mean_temps, 
        aes( x = Date_Time, y = Temp, 
             group = Site, color = -Lat, fill = -Lat ) ) +
  geom_smooth( method = "loess", se = T ) +
  scale_color_viridis_c() +
  scale_fill_viridis_c( guide = FALSE ) +
  labs( x = "Date", y = "Temp (°C)" , color = "Latitude (°N)" ) +
  theme_classic()

# Plot distributions of daily, grouped by site
ggplot( data = mean_temps, 
        aes( x = Lat, y = Temp, group = Site ) ) +
  geom_jitter( size = 0.5, width = 0.1, color = "grey" ) +
  geom_point( data = site_temps, size = 3 ) +
  geom_errorbar( data = site_temps,
                 aes( ymin = Temp - ci, ymax = Temp + ci ),
                 width = 0, size = 1 ) +
  labs( y = "Temp (°C)" , x = "Latitude (°N)" ) +
  geom_line( data = site_temps, group = "identity" ) +
  theme_classic() +
  theme( legend)

# Plot relationship between latitude and temp by month and year: latitudinal temp gradient only holds in winter months
ggplot( data = mean_temps, 
        aes( x = Lat, y = Temp, group = Site ) ) +
  geom_jitter( size = 0.5, width = 0.1, color = "grey" ) +
  geom_line( data = site_month_temps, group = "identity" ) +
  geom_point( data = site_month_temps, size = 3, aes( color = Temp ) ) +
  facet_wrap( ~Month, scale = "free" ) +
  scale_color_viridis_c() +
  labs( y = "Temp (°C)", x = "Latitude (°N)", color = "Temp (°C)" ) +
  theme_classic() +
  theme( strip.background = element_blank() )

```

```{r}

#Filter dates

mean_temps$Site = factor(
  mean_temps$Site,
  levels=c("BMR", "SC", "RMR",  "PTD"))

#Fig 3B
site_means <- summarySE(measurevar = "Temp",
                        groupvars = c("Lat", "Site"),
                        data = filter(mean_temps, 
                                      Date_Time > as.POSIXct("2020-12-31") &
                                        Date_Time < as.POSIXct("2022-01-01"))) 

#Fig 3A (map)
CA_df <- filter(map_data("state"), region == "california")

site_df <- data.frame(Site = c("BMR", "SC", "RMR", "PTD"),
                      lat = c(38.316375,
                              36.965681,
                              35.540147,
                              34.002089),
                      long = c(-123.071939,
                               -122.125905,
                               -121.092432,
                               -118.805022))

Fig_3A <- ggplot() + 
  geom_polygon(data = CA_df, aes(x = long, y = lat, group = group), fill = "gray") +
  geom_point(data = site_df, aes(x = long, y = lat, color = -lat), size = 8) +
  theme_classic(base_size = 20) +
  scale_color_viridis_c(guide = "none") +
  theme(legend.background = element_rect(fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        strip.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", color = NA)) +
  labs(y = "Latitude (°N)", x = "Longitude (°W)")
  
Fig_3A

# Fig 3B
Fig_3B <- ggplot(data = site_means,
                 aes(x = Temp, y = Lat, color = -Lat)) +
  geom_point(size = 4) +
  geom_errorbar(aes(xmin = Temp - ci, xmax = Temp + ci), 
                width = 0, size = 0.75) +
  theme_classic(base_size = 20) +
  theme(legend.background = element_rect(fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        strip.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", color = NA)) +
  scale_color_viridis_c(guide = "none") +
  labs(x = "Mean annual temp (°C)", y = "Latitude (°N)")

Fig_3B

#Fig 3C
Fig_3C <- ggplot(data = mean_temps,
                 aes(x = Date_Time, y = Temp, group = Site, 
                     color = -Lat)) +
  geom_hline(yintercept = 21.55, lty = 2, color = "red", 
             size = 0.75, alpha = 0.5) +
  geom_hline(yintercept = 16.42, lty = 2, color = "blue", 
             size = 0.75, alpha = 0.5) +
  geom_rect(aes(ymax = Inf, ymin = -Inf, 
                xmin = as.POSIXct("2021-06-17"),
                xmax = as.POSIXct("2021-08-06")),
            fill = "gray70", alpha = 0.1, color = NA) +
  geom_rect(aes(ymax = Inf, ymin = -Inf, 
                xmin = as.POSIXct("2021-12-28"),
                xmax = as.POSIXct("2022-02-16")),
            fill = "gray70", alpha = 0.1, color = NA) +
  geom_point(size = 0.5) +
  facet_grid(Site~.) +
  theme_classic(base_size = 20, base_rect_size = 0) +
  theme(legend.background = element_rect(fill = "transparent"),
        panel.background = element_rect(fill = "transparent"),
        strip.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", color = NA)) +
  scale_color_viridis_c(guide = "none") +
  labs(x = "Date", y = "Mean daily temp (°C)")

Fig_3C

#Arrange and export
Fig_3 <- ggarrange(Fig_3A, Fig_3B, Fig_3C, 
                   labels = c("", "", ""),
                   widths = c(1.25, .65,.85),
                   ncol = 3, nrow = 1, align = "hv")

Fig_3

# Export Fig 5 as png
# Export poster fig 2
ggsave(Fig_3,
       units = "in", width = 12, height = 6, 
       filename = "~/Documents/WSN_23_Fig1.png",
       bg = "transparent")

```

